Total Platform Cyber Protection

### 2016-06-25 paper.tex
proofread 8.2.4, left comments

Mitigation and recovery is of major concern when it comes to application and systems security. This area of research is important because recovery of a tainted system is the first concern post attack or exploitation.

Researchers have found some VM-based approaches in order to recover from intrusions.~\cite{zhang2009b} suggest one such approach. They try to achieve recovery in three phases, Routine execution phase, Damage assessment phase and Recovery phase. This framework tries to log pre-attack states and system calls and takes forward or reverse taint-tracking approach. Recovery phase tries to Quarantine the malicious files and objects identified during the Damage assessment.

A similar VM-based approach is taken in~\cite{oliveria2008b}. The Bezoar framework proposed in this paper tries to recover a system based on monitoring of propagation bytes in the system after hijacking attack has been detected. The framework replays the checkpointed run while ignoring inputs from malicious sources.

Automated intrusion recovery system is proposed in~\cite{goel2005b}. Researchers have designed automated resolution policies which determines set of tainted files. Taser recovery system~\cite{goel2005b}, is designed based on following models. Recovery model, Audito, Analyzer and Resolver. Techniques like naming conventions and file permissions, logging of all events, dependency of files, process and sockets are used by Taser in order to analyze intrusion. Similar to Recovery phase approach taken in~\cite{zhang2009b}, Taser uses the Resolver model proposed to go back to the state of the operating system before intrusion.

>>>>

Mitigation and recovery is a major area of concern when it comes to application security. 
% needs sentence about importance of mitigation
This is because recovery of a tainted system is the first concern post attack or exploitation.

%% TODO: this needs more stuff about mitigation, theres nothing about mitigation here.
%% TODO: this para needs grammar-check: check usage of commas, colons, etc.
%% TODO: in order to --> to, repetitive word `tries'
%% TODO: expand VM at least first time of usage, abbreviate it after
Researchers have found some VM-based approaches in order to recover from intrusions.~\cite{zhang2009b} suggest one such approach. They try to achieve recovery in three phases, Routine execution phase, Damage assessment phase and Recovery phase. This framework tries to log pre-attack states and system calls and takes forward or reverse taint-tracking approach. Recovery phase tries to Quarantine the malicious files and objects identified during the Damage assessment.

%% TODO: this has passive voice, try to avoid it
A similar VM-based approach is taken in~\cite{oliveira2008b}. The Bezoar framework proposed in this paper tries to recover a system based on monitoring of propagation bytes in the system after hijacking attack has been detected. The framework replays the checkpointed run while ignoring inputs from malicious sources.

%% TODO: grammar-check
Automated intrusion recovery system is proposed in~\cite{goel2005b}. Researchers have designed automated resolution policies which determines set of tainted files. Taser recovery system~\cite{goel2005b}, is designed based on following models. Recovery model, Audito, Analyzer and Resolver. Techniques like naming conventions and file permissions, logging of all events, dependency of files, process and sockets are used by Taser in order to analyze intrusion. Similar to Recovery phase approach taken in~\cite{zhang2009b}, Taser uses the Resolver model proposed to go back to the state of the operating system before intrusion.
